Towards Transparency and Open Science

### 2023-01-06 manuscript.Rmd
take a look at the cross-validation section

In addition to closeness to truth, there is another line of argumentation about why transparency about the process of induction is important.
Instead of verisimilitude, one might be concerned with future performance.
That is, how well does a theory do in predicting novel facts.
Please note that the information-theoretic setup above has made no appeal to the expected performance on unseen data.
Verisimilitude and expected performance are different motivations for transparency, though they can be linked.
In the future performance setup, we do not appeal to ground truth, replace the Kullback–Leibler divergence with an arbitrary loss function, and no longer require $g(x)$ to return probabilities:

@@

Still, the core problems of limited sample and inductive process remain.
Again there exists only a sample $y$ over which we form the expectation, but now we must pay a little more attention to the individual elements, $i = 1, \dots,n$ and take the expectation [@sochLawUnconsciousStatistician2020]:

@@

$$
\mathbb{E}_y L(y, g(y|\theta))
 = \frac{1}{n}\sum_{i=1}^n L(y_i, g(y_i|\theta))
$$

Instead of using the Taylor series expansion, we can repeatedly sample data and repeat the inductive process.
That is, we make use of cross-validation where the data is partitioned, and the inductive process is repeated on all permutations of a subset of the partitions.
For each subset, the resulting model is then compared to the complement that was not used for induction, which is indicated by $y_{-i} = y \diagdown \{y_i\}$.

$$
\mathbb{E}_{x \sim f} L(x, g(x|\hat\theta(y)))
 = \frac{1}{n}\sum_{i=1}^{n}L(y_i, g(y_i|\hat\theta(y_{-i})))
$$

As stated earlier, using cross-validation we can also estimate the If we reinstate Kullback-Leibler divergence as a loss function, we can estimate $\mathbb{E}_y\mathbb{E}_x[log(g(x|\hat\theta(y)))]$ using the cross-validatory which connects the information-theoretic setup with this approach [@stoneAsymptoticEquivalenceChoice1977; @stoneCrossValidatoryChoiceAssessment1974].
To make the link to the first approach even more clear, we may define complexity in these terms [@hauensteinComputingAICBlackbox2018]:

>>>>

In addition to closeness to truth, there is another line of argumentation about why transparency about the process of induction is important.
Instead of verisimilitude, one might be concerned with future performance.
That is, how well does a theory do in predicting novel facts.
Please note that the information-theoretic setup above has made no appeal to the expected performance on unseen data.
Verisimilitude and expected performance are different motivations for transparency, though they can be linked.
In the future performance setup, we do not appeal to ground truth, replace the Kullback–Leibler divergence with an arbitrary loss function, and no longer require $g(x)$ to return a likelihood:

@@

Again we can define the loss we have observed in the sample used to estimate $\hat\theta$ [@sochLawUnconsciousStatistician2020]:

@@

$$
\mathbb{E}_y L(y, g(y|\hat\theta(y)))
 = \frac{1}{n}\sum_{i=1}^n L(y_i, g(y_i|\theta))
$$

However, what we are interested in is not how well the theory did on data that informed it but on future, yet unseen, data:

$$
\mathbb{E}_x\mathbb{E}_yL(x, g(x|\hat\theta(y)))
$$
This expectation over, what is often called training and test data, is termed generalization error or expected prediction error [@bengioNoUnbiasedEstimator2004] and resembles the expectation over data discussed in the information-theoretic setup [@stoneAsymptoticEquivalenceChoice1977].
Instead of using the Taylor series expansion, we can repeatedly sample data and repeat the inductive process.
That is, we make use of cross-validation where the data is partitioned, and the inductive process is repeated on all permutations of a subset of the partitions.
For each subset, the resulting model is then compared to the complement that was not used for induction, which is indicated by $y_{-i} = y \diagdown \{y_i\}$.

$$
\mathbb{E}_{x}\mathbb{E}_{y}  L(x, g(x|\hat\theta(y)))
 = \frac{1}{n}\sum_{i=1}^{n}L(y_i, g(y_i|\hat\theta(y_{-i})))
$$

As stated earlier, using cross-validation we can also estimate \nobreak\hfil\penalty0 \hfilneg $\mathbb{E}_{X \sim f}\mathbb{E}_{Y \sim f^n}[log(g(x|\hat\theta(y)))]$ which connects the information-theoretic setup with this approach [@stoneAsymptoticEquivalenceChoice1977; @stoneCrossValidatoryChoiceAssessment1974].
To make the link to the first approach even more clear, we may define complexity in these terms [@hauensteinComputingAICBlackbox2018]:
